\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in R

### 2014-01-21 papers/jss/article.Rnw
Add an initial conclusions and commentary section.
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@810 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

\section{Summary}
\label{sec:summary}

TODO RProtoBuf is quite flexible and easy to use for interactive
analysis, but it is not designed for certain classes of operations one
might like to do with Protocol Buffers.  For example, taking a list of
10,000 Protocol Buffers, extracting a named field from each one, and
computing a aggregate statistics on those values would be extremely
slow with RProtoBuf, and while this is a useful class of operations,
it is outside of the scope of RProtoBuf.  We should be very clear
about this to clarify the goals and strengths of RProtoBuf and its
reflection and object mapping.

%\section{Other approaches}

% Phillip Yelland wrote another implementation, currently proprietary,
% that has significant speed advantages when querying fields from a
% large number of protocol buffers, but is less user friendly for the
% basic cases documented here.

% RProtoBuf has been used.

%Its pretty useful.  Murray to see if he can get approval to talk a
%tiny bit about how much its used at Google.

%This file is only a basic article template. For full details of \emph{The R Journal} style and information on how to prepare your article for submission, see the \href{http://journal.r-project.org/latex/RJauthorguide.pdf}{Instructions for Authors}.

>>>>

\section{Conclusion and Commentary}
\label{sec:summary}
% TODO(mstokely): Get cibona approval for these two sentences before
% publishing.
Schema-less text formats such as CSV and JSON will continue to be
widely used in many contexts, but we hope that the availability of
\pkg{RProtoBuf} makes it easy for many mixed-language data analysis
pipelines to embrace schemas such as Protocol Buffers for type-safe
and performant data serialization between applications.

\pkg{RProtoBuf} has been heavily used inside Google for the past three
years by statisticians and software engineers.  At the time of this
writing there are more than XXX 30-day active users of RProtoBuf using
it to read data from and otherwise interact with other distributed
systems written in C++, Java, Python, and other languages.

\paragraph*{Other Approaches}

\pkg{RProtoBuf} is quite flexible and easy to use for interactive use,
but it is not designed for efficient high-speed manipulation of large
numbers of protocol buffers once they have been read into R.  For
example, taking a list of 100,000 Protocol Buffers, extracting a named
field from each one, and computing an aggregate statistic on those
values would be relatively slow with RProtoBuf.  Instead for such a
use case, the current design of RProtoBuf relies on other database
systems to provide query and aggregation semantics before the
resulting protocol buffers are read into R.  Such queries could be
supported in a future version of \pkg{RProtoBuf} by supporting a
vector of messages type such that \emph{slicing} operations over a
given field across a large number of messages could be done
efficiently in C++.
